\documentclass{paper}

\begin{document}

\title{%
Trusting Web Media \\
\large A decentralized content scoring system in the browser and blockchain}

\author{Christopher Dieringer}

\maketitle
\newpage

\section{Abstract}
The creation of and spread of false information has led to
a grand public scare, leaving constitiuents fearful of trusting
reported media.  For example, when polarized claims are made by oppositional
sources, there are few objective or subjective tools offered to consumers
on how to reconcile the conflict.  Reconciling truth is essential to
team building and problem solving, which we rely on at the local and national
level to advance our society and relationships.  Without a trust model, the
information we can trust is a much smaller subset from the whole truth,
preventing us from making well-informed decisions and reaching agreement with
our equally constrained peers.  We present a scoring model that is embedded with
all web-based media, that provides consumers real-time metadata about the
trustworthiness of the visible or audible content.  Poor scoring media is
presented behind entry points which warn the user prior to digestion.  Other
media scores are presented at the domain, page, or even DOM-element level,
allowing consumers to proceed with digestion on an informed basis.

A secondary driver for this work is the progression of synthesized video and
synthesized audio, specifically those synthesizing artificial human communication.
These technologies pose a
serious threat undermining trust in all medias, beyond face-to-face or physical
communication.  Because the web is humanity's dominant media communication
mechamism, we believe that a technology trust model is highly relavant
to protect our core values.

\section{Problem}

False information is rampant <cite> and creates disagreement among parties who
ultimately seek similar objectives <cite, iirc this-american-life had some good sources here>.
\begin{itemize}
  \item enumerate multiple false information campaigns and their successes
  \item enumerate popular myths that still hold as truths to consumers today
  \item discuss how the web's prominenet role enabled the spread
\end{itemize}

In a world of untrust, one could define the root problem as the simple notion
that people lie.  The reasons for lying, or even simply misreprenting the
truth, are not covered or discussed here.  We take this unfortunate reality as
a core assumption and input into our problem.  A secondary problem is that the
output from the primary problem is easily and quickly dispersable on the web.
The easy of dispersability of information, however, is also the core strength of
the web.  Whilst the problem could be addressed here, it is censorship, and the
authors believe censorship to generally be a threat to society versus a helping
hand.  A tertiary problem from the above two is that the transmitted information
is likely to be trusted even from an untrustworthy source.  We assume
cryptographic security to be already in place for all of these communications,
as that is a well researched and documented problem space already.  Because we
will not silence voices who falsify or bend truth, and because we will not
cut off access to such voices, we believe improving the digestion of all
media is an ideal candidate.

\section{Existing Solutions}

\begin{itemize}
  \item discuss fact checking campaigns, companies, individuals
  \item ==> express why these are retroactive, and why they poorly stop digestion-as-truth
  \item discuss centralized rating systems, independents, and why there will always be reason to cast doubt
\end{itemize}

\section{Solution - WebTrust}

\paragraph{Overview}
\begin{itemize}
  \item WebTrust is predominantly a browser feature.  It
  extends the existing HTML DSL, enhancing web media by applying non-developer
  editable, visual metadata about the media, supported from decentralized score
  data living on the blockchain.
  \item WebTrust uses the decentralized web to uniquely identify individual humans, individual pieces of media
  \item Humans tag media as (un)authentic.  These are generally people who witnessed the published media as well.
  \item Media providing humans gain reputation score based on authenticty
\end{itemize}

\paragraph{HTML}
\begin{itemize}
  \item Forbids non-children elements to be rendered within container
\end{itemize}


\section{Conclusion}

\subsection{}
\subsubsection{}

\paragraph{}
\subparagraph{}

\end{document}
